The Quench-Action method in integrable spin chains: A Monte Carlo approach

### 2015-09-11 draft/fs_qa_v1.tex
final

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\textwidth]{./draft_figs/Neel_overlaps}
\end{center}
\caption{ 
}
\label{fig0}
\end{figure}
%##################################################################

>>>>

%##################################################################
\begin{figure}[t]
\begin{center}
\includegraphics[width=.9\textwidth]{./draft_figs/Neel_overlaps}
\end{center}
\caption{ N\'eel state overlaps in the Heisenberg spin chain. (a) 
 The N\'eel state overlaps with the eigenstates of the Heisenberg 
 spin chain: Squared overlaps $|\langle\lambda|N\rangle|^2$ plotted 
 as a function of the eigenstates energy density $E/L$. Here $|\lambda
 \rangle$ denotes the generic eigenstate of the Heisenberg spin chain. 
 The data are for chains with length $26\le L\le 38$. The data are 
 obtained from a full scanning of the chains Hilbert space. 
 Eigenstates containing strings with zero-momentum components 
 are escluded. The overlaps decay exponentially with the chain size. 
 (b) Histograms of $-2\log|\langle\lambda|N\rangle|/L$. Different 
 histograms are for different chain sizes. The histogram bin width 
 is $\sim 2/L$. The $y$-axis is rescaled by a factor $10^5$ for 
 convenience. Note the peaking of the histograms around 
 $-2\log|\langle\lambda|N\rangle|\sim 0.5$ in the thermodynamic 
 limit {\bf really??}. 
}
\label{fig0:N-ov-overview}
\end{figure}
%##################################################################
